BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-02 tex/3-algorithms.tex
Up

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

@@

% assumptions when working with blogs
Having blogs as our target websites, the assumptions we made and which play a central role in the extraction process are the following\Anote{assumptions}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the most recent posts of a blog,\TODO{mention RSS and Atom, just to confirm to the reader what a web feed is?}
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 posts\cite{oita2010},\TODO{Add more info on web feeds, merge with the text on intro.} often less than the total number of posts in blogs. Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
\TODO{When I read this section for the first time, I was confused.
After I also read 3.3 and 3.4 I understood better.
You should have a nicely structured overview of the algorithm in 3.2 and have references for 3.3 and 3.4
When you describe the algorithm overview, you should say explicitly that function X and operation Y is explained in section Z, etc}
% per blog procedure, related work
To extract content, authors, dates and comments from blog posts, we started by building extraction rules from the data given in the blog's web feed. \TODO{These rules take advantaged of the facts presented in 3.1 to create a more efficient data extraction process, outperforming more generic extraction algorithms that work directly with HTML pages.}These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog. This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.\comment{This might be a bit too raw, give more context at this point?}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}\label{motivation}
% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

@@

% assumptions when working with blogs
Having blogs as our target websites, we use the following observations \TODO{If ok, change everywhere else.} which play a central role in the extraction process\Anote{assumptions}:  
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs. \TODO{Add more info on web feeds, merge with the text on intro?} Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
\TODO{When I read this section for the first time, I was confused.
After I also read 3.3 and 3.4 I understood better.
You should have a nicely structured overview of the algorithm in 3.2 and have references for 3.3 and 3.4
When you describe the algorithm overview, you should say explicitly that function X and operation Y is explained in section Z, etc}

% per blog procedure, related work
To extract articles, authors, dates and comments from blog posts, we procede by building extraction rules from the data given in the blog's web feed. Concretely, this procedure takes as input a set of pairs of HTML pages and target contents. It will then search for an extraction rule that jkjhkjhkjhkjhkjhkjhkjh

This rule is such that when applied to other input pages, the extracted contents are as similar as possible to the corresponding target contents.\TODO{You definitely need a better explanation}

These rules take advantaged of the assumption presented in \ref{motivation} to create a more efficient data extraction process, outperforming more generic extraction algorithms that work directly with HTML pages \cite{gkotsis2013}, \cite{oita2010}.

These rules take advantage of our assumption that the HTML structure between different posts of the same blog is the same, in order to be applicable to all the posts of a blog. This approach has been examined in the past and has demonstrated great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that work directly on HTML pages.
